In this section, the models described in this report are compared with the performance profile tool provided. Several runs were carried out to fully test the models for a more accurate conclusion. In particular, the best algorithm is the one that finds the optimal solution in the shortest time for most of the time. While analyzing the metaheuristics approaches it is impossible to compare them in a time scale, so instead of the time the comparison here is done between the cost of the solution obtained.

Since the TSP is a NP-hard problem, finding a winner is not always easy. Sometimes different methods can lead to very similar results, so several factors - such as consistency - are took in consideration.

To discuss, the outcome of the tests is plotted and so it is needed some explanation on how to understand them. While the x-axis portrays the time (or cost) ratio which will show what algorithm performs better, the y-axis shows the fraction of instances that the algorithm ends up winning. In general, the best method is the one that remains more on the left side of the chart.

As explained in section \ref{sec:solution-data-management}, the TSPLIB is used only to carry out if the implemented algorithms can reach the optimal value. To run these tests, a series of randomly generated instances are used.

\section{Compact models}
\label{sec:results-compact}
\input{results/compact_models.tex}

\section{SEC methods}
\label{sec:results-sec}
\input{results/sec.tex}

\section{Matheuristics}
\label{sec:results-math}
\input{results/matheuristic.tex}

\section{Metaheuristics}
\label{sec:results-heur}
\input{results/metaheuristics.tex}

\section{Conclusions}
\label{sec:conclusions}
\input{results/conclusion.tex}