Section \ref{chapter:primo_capitolo} described the problem and stated that it is NP-hard. The computational effort to obtain an optimal solution to this problem is high. Due to this fact, the implementation will be done using the programming language C which will provide really good efficiency and better memory management than other languages.

All the results obtained in this report were executed on a Linux machine with Ubuntu 20.04 as operative system. The system runs an Intel Core i7 8550u @1.80Ghz with 16Gb of RAM.

To produce this code, lots of software were used. The main IDE in this project is CLion by IntelliJ and CMake is the build software adopted to compile the code. The most important software used is IBM ILOG CPLEX, which is an optimization software package integrated in the code through its Callable Library (API). This software isn’t usually free but it was made available free of charge for students that needed it for academic purposes.

During this project, the TSP problem could present some fractional solution, and to deal with them the external library Concorde has been used (furter explaination in section \ref{chapter:callback-fractional}).

The Gnuplot library, which is a command-line driven utility, was adopted to visualize the solution found. The main usage was to check the effect of the code written to the TSP instances. The graphs of this report are generated exploiting the command line and using Gnuplot through a pipe.

For analyzing the efficiency of the algorithms presented, a performance profile tool has been used. This tool is written by Salvagnin (2019) and it is for internal use only.

\section{Solution and data management}
\input{code_setup/solution_data_management.tex}


\section{CPLEX's variables and constraints}
\input{code_setup/cplex_variables_constraints.tex}
